### 2024-02-23 documentation/thesis/thesis_document.tex
.

\gls{mri} stands as a cornerstone in clinical diagnostics, utilizing the
principles of nuclear magnetic resonance \gls{nmr} to generate
cross-sectional black-and-white images of the body. This indispensable
method plays a significant role in contemporary medicine and research,
contributing significantly to saving lives. Despite its widespread use,
traditional \gls{mri} systems often rely on large, heavy, and expensive
magnets to achieve the necessary homogeneity of the magnetic field for
accurate imaging. \customcite{NK16}

Several types of magnets are applicated in different \gls{mri} systems.
Permanent magnets generate a steady yet relatively weak magnetic field,
electromagnets are energized by electrical currents and superconducting
electromagnets produce magnetic fields through electric induction.
Regardless of the type, the primary objective is to create a homogeneous
magnetic field within the \gls{mri}. The higher the homogeneity, the
more accurate the measurements. Homogeneity in composed \gls{mri} can be
adapted using the shimming procedure which requires a lot of effort and
is prone to errors. This uniform magnetic field aligns the molecules
within the body or object, setting the stage for a second magnetic
system to stimulate these molecules for spin-measurements.

@@

The challenge with conventional homogeneity systems lies in their
substantial size, weight, and cost. Even when targeting smaller areas of
the body, large devices are often necessary. In response to this, there
is a growing interest in developing low-field \gls{mri} systems that
utilize in many cases permanent magnets. These systems, while offering
advantages in energy efficiency and reduced complexity, face a
significant challenge related to the inherent variability in the
strength of permanent magnets. Achieving homogeneity in the magnetic
field is crucial for accurate imaging or comparative analyses. While
typically calculated images have lower resolution due to lower magnetic
field strength, low-field systems facilitate the comparison of different
field behaviours and the identification of all kinds of irritations.
O'Reilly and Teeuwisse and de Gans \customcite{OTW19} have already
demonstrated low-cost and small-scale implementations with low-field
\gls{mri} in 2021 calculating images of a head successfully.

@@

For modern medical imaging high-field superconducting magnets dominate
most \gls{mri} machines, providing in general a higher image contrast.
The substantial costs, space requirements and safety and installation
considerations cause considerable challenges.

\gls{mri} relies on the presence of a robust magnetic field, and over
time, there has been a continual push to enhance the strength of these
magnetic fields. This strength is quantified in units of Tesla {[}T{]},
commonly referred to as the \emph{B0} field in medical contexts, while
physicists use the term magnetic field induction. The \gls{snr} is
proportional to the magnetic \emph{B0} field; growing magnetic field
leads automatically to higher \gls{snr}. The initial \emph{B0} field of
an \gls{mri} aims to be homogeneous, for image acquisition the second
step requires inhomogeneity of the \emph{B0} field to stimulate spin in
the atoms of materials. For high resolution images, the initial
\emph{B0} field aims to be a homogeneous as possible.

@@

This technology is used in medical imaging as well as in preclinical
research. The main advantage of low-field \gls{mri}s is the improved
imaging of soft material, especially when examining joints and muscles.
It also offers more cost-effective alternatives to high-field \gls{mri}
systems \customcite{HH21}, cost reduction, a smaller device footprint,
alleviated safety concerns and leading to diminished image resolution
within clinically feasible scan durations. \customcite{AFL23}

Low-field \gls{mri} systems are predominantly composed of permanent
magnets. Through the connection of these permanent magnets, a consistent
magnetic field of up to \emph{0.35T} can be generated. However, this
achievement comes at the cost of an average system weight of \emph{14t}.
Despite their cost-effectiveness in production and maintenance,
permanent magnets show drawbacks such as high temperature dependence and
a limited \gls{snr} due to the constrained field strength.
\customcite{NK16}

@@

A Halbach ring of this type is usually based on a ring with permanent
magnets arranged in a circle. The Figure
\ref{Example_Halbach_ring_with_cutouts_for_eight_magnets.png} shows an
example \gls{cad} model of such a ring.

@@

The sources for the shimming process can be hardware and software based.
Hardware shimming involves the use of gradient and radio frequency coils
that are specifically placed to align the magnetic field.
\customcite{BPA22} Software shimming, on the other hand, uses algorithms
to adjust the control parameters of the \gls{mri} system and improve
homogeneity \customcite{WAH21}.

@@

The Halbach magnet incorporated in this system boasts a \emph{27cm}
diameter, a \emph{B0} field strength of \emph{50.4 mT}, and an
impressive homogeneity of \emph{2400 \gls{ppm}} over a \emph{20cm}
diameter using smaller magnets (\(12 x 12 x 12 mm^3\)). This exceptional
homogeneity enables the utilization of coil-based gradients for spatial
encoding, significantly enhancing the flexibility of image acquisition.

@@

In order to measure the magnets individually, there are already
implementations that use different measurement methods to determine the
field strength of individual magnets and individual measuring points are
recorded. This data is then evaluated in separate software
\customcite{WZC21}.

@@

Special algorithms from various, public projects are used to optimize
homogeneity, like a genetic algorithm which O'Reilly implemented
\customcite{O24}. Therefore, the challenge is to ensure the seamless
integration and compatibility of these algorithms into the overall
process. This should make it possible to create a workflow from the
individual magnet to the finished optimized \gls{cad} model of a Halbach
ring.

@@

Two sensors have been meticulously chosen for inclusion in the study.
The ultimate objective is to assess whether these selected sensors align
with the stringent criteria of achieving an accuracy level of \emph{1000
\gls{ppm}}. Furthermore, the study seeks to validate whether the
measuring range of these sensors appropriately corresponds to the
required field strength, ensuring their suitability for the intended
application.

@@

Concerning the \emph{DeLoRI} project, this study exclusively delves into
the realm of permanent magnets employed for creating a homogeneous
\emph{B0} field through Halbach rings. Other systems and spin generation
for measurements are deliberately excluded from consideration but will
be necessary in later stages of the \emph{DeLoRI} project.

@@

The Figure
\ref{Typical_block_diagram_of_a_digital_hall_sensor_sensing_chain_using_three_hall_plates.png}
shows the internal structure of a digital Hall effect sensor as a block
diagram. The Hall effect takes place in the Hall plates. These are
orientated differently depending on the axis inside the \gls{ic}s. In
this case, it is a three-axis hall effect sensor. The output voltage
generated by the Hall plates is then digitised by a \gls{adc}. The
values can then be read out via a digital interface.

@@

\begin{longtable}[]{@{}lllll@{}}
\caption{List of in unified firmware implemented digital magnetic field
sensors with focus on different sensor capabilities.
\label{List_of_in_unified_firmware_implemented_digital_magnetic_field_sensors_with_focus_on_different_sensor_capabilities.csv}}\tabularnewline
\toprule
& TLV493D & HMC5883L & MMC5603NJ & AS5510\tabularnewline
\midrule
\endfirsthead
\toprule
& TLV493D & HMC5883L & MMC5603NJ & AS5510\tabularnewline
\midrule
\endhead
Readout-Axis & 3D & 3D & 3D & 1D\tabularnewline
Temperature-Sensor & yes & no & yes & no\tabularnewline
Resolution {[}uT{]} & 98 & 0.2 & 0.007 & 48\tabularnewline
Range {[}mT{]} & ±130.0 & ±0.8 & ±3 & ±50\tabularnewline
Interface & \gls{i2c} & \gls{i2c} & \gls{i2c} & \gls{i2c}\tabularnewline
\bottomrule
\end{longtable}

@@

The Table
\ref{List_of_in_unified_firmware_implemented_digital_magnetic_field_sensors_with_focus_on_different_sensor_capabilities.csv}
shows a selection of sensors for which hardware and software support has
been implemented. The resolution of the selected sensors covers the
expected range of values required by the various magnets to be tested.

@@

Figure
\ref{Rendered_mechanical_structure_of_the_1D_sensor_(+cad)_model_with_different_parts_colored_separately,_and_universal_magnet_mount_shown_in_green.png},
shows rendered view of the 1D-Single sensor \gls{cad} drawing, which is
described in chapter \ref{d-single-sensor}. All parts are produced using
3D printing additive manufacturing process. The sensor circuit board is
glued underneath the magnet holder. This is interchangeable, so
different distances between sensor and magnet can be realised. The
exchangeable magnetic holder (shown in green in Figure
\ref{Rendered_mechanical_structure_of_the_1D_sensor_(+cad)_model_with_different_parts_colored_separately,_and_universal_magnet_mount_shown_in_green.png})
can be adapted to different magnets. It can be produced quickly due to
the small number of parts used. The two recesses lock the magnet holder
with the inserted magnet over the sensor. The specified tolerances allow
the magnet to be inserted into the holder with repeat accuracy and
without backlash. This is important if several magnets must be measured,
where the positioning over the sensor must always be the same.

@@

The Figure
\ref{Unified_sensor_firmware_program_structure_with_listed_setup_and_main_loop_routines_using_simplified_function_blocks.png}
shows a flow chart of the start process after powering on the sensor and
the subsequent main loop for processing the user commands and sensor
results. When the microcontroller is started, the software checks
whether known sensors are connected to \gls{i2c} or \gls{uart}
interfaces.

@@

\begin{itemize}
\tightlist
\item
  \gls{mrp}-library, explained in chapter
  \ref{software-readout-framework}
\item
  Stand-alone mode via sending commands using built-in \gls{cli}
\end{itemize}

The \gls{cli} mode is a simple text-based interface with which it is
possible to read out current measured values, obtain debug information
and set operating parameters. This allows to quickly inspect whether the
hardware is working properly after firmware installation. The command
\emph{help}, displays a detailed command reference with all available
commands as shown in the Figure
\ref{Unified_sensor_firmware_provided_serial_terminal_based_(+cli)_allows_the_user_to_configure_the_sensor_manually.png}
to the user.

@@

The Figure
\ref{Result_of_an_executed_b_value_measurement_readout_command_using_the_sensors_(+cli)_with_immediate_user_readable_response.png}
shows the current measured value queried by using the \emph{readout}
command by the user.

@@

A jitter time of up to an additional \emph{1ms} is added between the
triggering of the measurements by the host system and the receipt of the
command by the sensor hardware. If the host system is still under load,
this value increases many times over. This means that synchronising
several sensors via the \gls{usb} connection alone is not sufficient.
The other issue is sending the trigger signal from the readout software,
which is described in chapter \ref{software-readout-framework}. At this
point unpredictable latencies can occur, too, depending on which other
tasks are also executed on this port. To enable the most stable possible
synchronisation between several sensors, an option has already been
created to establish an electrical connection between sensors. This is
used together with the firmware to synchronise the readout intervals.
The Figure
\ref{Multi_sensor_synchronisation_wiring_example_using_three_sensors_together_with_one_host_(+pc)_performing_the_triggering_and_readout_processing.png}
illustrates the schematic how several sensors must be wired together to
implement this form of synchronisation.

@@

Once the hardware has been prepared, the task of the firmware of each of
the chained sensors is to find a common synchronisation clock. The
Figure
\ref{Unified_sensor_firmware_multi_sensor_synchronisation_procedure_using_sync_(+gpio)_input_for_operation_(primary_or_secondary)_mode_decision.png}
illustrates how the firmware handles the decision task if the sensor is
\emph{primary} or \emph{secondary} at startup. The internal
firmware-function \emph{register irq on sync pin} is overwritten. To set
one \emph{primary} and several \emph{secondary} sensors, each sensor
waits for an initial pulse on the SYNC-\gls{gpio}, which is a pin at the
microcontroller with the functionality to detect if the sensor is a
primary or a secondary sensor. A random timer is started beforehand by
each sensor, which sends a pulse on the sync line. All others receive
this and switch to \emph{secondary mode} and synchronise the
measurements based on each sync pulse received.

@@

In single-sensor operation, this automatically jumps to \emph{primary}
sensor operation through the \emph{got impulse within 1000ms} branch
result. The Figure
\ref{Result_of_the_opmode_command_execution_on_a_sensor_which_is_connected_to_another_as_primary_configured_sensor.png}
shows the synchronisation status of the sensor which can be queried via
the user interface described in chapter \ref{communication-interface} by
using the \emph{opmode} command. An important aspect of the
implementation is that there is no numbering or sequence of the
individual sensors. This means that for the subsequent readout of the
measurements, it is only important that they are taken at the same
interval across all sensors. The sensor differentiation takes place
later in the \gls{mrp}-library \ref{software-readout-framework} by using
the sensor \gls{uuid}.

@@

The Table
\ref{Build_hardware_sensors_equipped_with_different_sensor_(+ic)s_to_cover_various_magnet_charaterisation_setups.csv}
shows the various prototype sensor platforms equipped with different
magnetic field sensors. These cover all the required functions described
in the use cases \ref{use-cases}. The most significant difference, apart
from the sensor used, is the \emph{scan mode}. In this context, this
describes whether the sensor can measure a \emph{static} fixed point on
the magnet or if the sensor can move \emph{dynamically} around the
magnet using a controllable manipulator.

@@

The Figure
\ref{3D_plot_of_an_N45_12x12x12mm_magnet_using_the_build_3D_full_sphere_sensor_with_visible_magnetic_field_strength_deviations_using_different_shaded_vertices_on_a_sphere.png}
shows the visualisation of such a scan in the form of a spherical 3D
map. On the sphere is the magnetic field strength, which is detected by
the sensor at the position. The transition from a fully positive field
strength (red) to a negative field strength (blue) is clearly
recognisable and corresponds to the orientation of the magnet in the
holder. The magnet sensor is mounted on a movable arm, which can move
\emph{180} degrees around the magnet on one axis. To be able to map the
full sphere, the magnet is mounted on a turntable. This permits the
manipulator to move a polar coordinate system.

@@

For this purpose, the library is divided into individual modules, which
are shown in the Figure
\ref{A_high_level_overview_of_all_MRP_library_implemented_Python_modules_which_can_be_changed_by_the_user.png}.
In combination, these represent a typical
measurement-analysis-evaluation workflow of data. For this purpose, a
module system with standardised functional patterns and data types is
developed and packed together in an extendable Python library.

@@

As it is possible to connect many identical sensors to one host,
therefore it needs to be possible to address them separately. This
separation is done by the \emph{MRPProxy} module, which is a separate
part from the core \gls{mrp}-library, to keep installation package
dependencies small. Each connected sensor is accessed via the text-based
\gls{cli}, which is initially the same for each sensor. The only
identification feature is the sensor \gls{uuid} by using the \emph{id}
command of the sensor \gls{cli}. The \emph{MRPProxy} instance claims to
be a sensor to the host \gls{pc} running \gls{mrp} \gls{cli}, so
multiple sensors must be combined into one virtual one. This is done in
several steps, the procedure described by the following sub-chapters.

@@

A crucial point is the management of the meta data, which further
describes the measurement. This is realised in the example using the
\emph{set\_additional\_data} function. Finally, the measurement is
exported for archiving and further processing; various export formats
are available. Using the \emph{dump\_to\_file} function, the measurement
can be converted into a open \gls{json} format.

@@

The main function of the \emph{MRPReading} module is to manage the
measurement and meta-data. The next step is to record and store real
sensor data. For this purpose, the \emph{MRPHal} module is developed,
which can interact with all \emph{Unified Sensor} compatible sensors
(refer to chapter \ref{unified-sensor}). In the following example
Listing \ref{lst:mrpexample_hal}, an \emph{1D: Single Sensor}, which is
explained in chapter \ref{d-single-sensor}, is connected locally to the
host \gls{pc}. \newpage

@@

The next logical step is to analyse the recorded data. This can involve
one or several hundred data records. Again, the procedure for the user
is to write their own evaluation Python scripts using the
\gls{mrp}-library. This is particularly useful for complex analyses or
custom algorithms, but not necessarily for simple standard tasks such as
bias compensation or graphical plot outputs. For this purpose, \gls{cli}
application is created further, to enable the user to create and execute
complex evaluation pipelines for measurement data without programming.
The Figure \ref{Example_measurement_analysis_pipeline.png} shows a
typical measurement data analysis pipeline, which consists of the
following steps:

@@

The documentation has also been uploaded to the
\href{https://magneticreadoutprocessing.readthedocs.io/}{ReadTheDocs}
service. The Figure
\ref{MagneticReadoutProcessing_documentation_hosted_on_ReadTheDocs.png}
shows a screenshot of the start page, which also lists separate menu
items for tutorials on the individual functionalities. The process of
creating and publishing the documentation has been automated using
\href{https://github.com/features/actions}{GithubActions}, so that it is
always automatically kept up to date with new features.

@@

The Figure
\ref{MRP_evaluation_result_after_find_similar_values_algorithm_execution_in_the_user_defined_pipeline.png}
shows the measured values filtered by the implemented filter algorithm
of Listing \ref{lst:custom_find_similar_values_algorithm}. It can be
seen that of the initial \emph{10} measurements (upper plot), only four
measurements that are most similar to the \emph{\gls{cog}} mean value
were filtered (lower plot). The number of desired result measurements
was defined here by the parameter \emph{IP\_return\_count}. It can be
seen from the plotted \emph{\gls{cog}} \(\mu\)T mean values values, that
these are closest to an ideal Magnet with a \emph{\gls{cog}} value of
0\(\mu\)T. This ideal value is calculated with the function
\emph{MRP.MRPSimulation.generate\_simulated\_reading}, with the same
measurement parameters (\emph{magnet type}, \emph{dimensions},
\emph{sensor distance}) as they correspond to the mechanical structure
of the used hardware sensor in chapter \ref{d-full-sphere}.

@@

The filter algorithm implemented by the user is thus successfully
executed via the user-programmable pipeline The calculation result was
successfully verified using raw measurement data and the result of the
algorithm and verified using reference measurements. The streamlined
pipeline approach enables the user to re-execute the implemented
measurement pipeline example with further measurement data. Changes to
filter parameters, for example, are also possible without having to
adapt the code. Using this example, all the required functional
capabilities from the chapter \emph{Use cases} \ref{use-cases} of this
implemented solution were demonstrated in their functional capability.

@@

For this evaluation, the sensors listed in the Table
\ref{Digital_magnetic_field_sensors_characterised_for_evaluation.csv}
are used for sensor characterisation. The selection of sensors is
described in chapter \ref{sensor-selection}. The additional column for
the \emph{Background Noise} is taken from the respective data sheets of
the sensors and will be verified in the later \emph{Background Noise}
measurement in chapter \ref{sensor-characterisation-background-noise}.

>>>>

\gls{mri} stands as a cornerstone in clinical diagnostics, utilizing the
principles of nuclear magnetic resonance \gls{nmr} to generate
cross-sectional images of the body. This indispensable method plays a
significant role in contemporary medicine and research, contributing
significantly to saving lives. Despite its widespread use, traditional
\gls{mri} systems often rely on large, heavy, and expensive magnets to
achieve the necessary homogeneity of the magnetic field for accurate
imaging. \customcite{NK16}

Several types of magnets are applicated in different \gls{mri} systems.
Regardless of the type, the primary objective is to create a homogeneous
magnetic field within the \gls{mri}. The higher the homogeneity, the
more accurate the measurements. Homogeneity in composed \gls{mri} can be
adapted using the shimming procedure which requires a lot of effort and
is prone to errors. This uniform magnetic field aligns the molecules
within the body or object, setting the stage for a second magnetic
system to stimulate these molecules for spin-measurements.

@@

The challenge with conventional homogeneity systems lies in their
substantial size, weight, and cost. Even when targeting smaller areas of
the body, large devices are often necessary with a higher field-strength
of at least 1.5 T. \customcite{HH21} In response to this, there is a
growing interest in developing low-field \gls{mri} systems that utilize
in many cases permanent magnets. Permanent magnets generate a steady yet
relatively weak magnetic field. These systems, while offering advantages
in energy efficiency and reduced complexity, face a significant
challenge related to the inherent variability in the strength of
permanent magnets. Achieving homogeneity in the magnetic field is
crucial for accurate imaging or comparative analyses. Low-field systems
facilitate the comparison of different field behaviours and the
identification of all kinds of irritations. O'Reilly, Teeuwisse and de
Gans \customcite{OTW19} have already demonstrated low-cost and small-scale
implementations with low-field \gls{mri} in 2021 calculating images of a
head successfully.

@@

For modern medical imaging high-field superconducting magnets dominate
most \gls{mri} machines, providing in general a higher contrast. The
substantial costs, space requirements and safety and installation
considerations cause considerable challenges.

\gls{mri} relies on the presence of a robust magnetic field, and over
time, there has been a continual push to enhance the strength of these
magnetic fields. This strength is quantified in units of Tesla {[}T{]},
commonly referred to as the \emph{B0} field in medical contexts, while
physicists use the term magnetic field induction. The \gls{snr} is
proportional to the magnetic \emph{B0} field; growing magnetic field
leads automatically to higher \gls{snr}. For high resolution images, the
initial \emph{B0} field aims to be a homogeneous as possible.

@@

This technology is used in medical imaging as well as in preclinical
research. The main advantage of low-field \gls{mri}s is the improved
contrasting of soft material. It also offers more cost-effective
alternatives to high-field \gls{mri} systems \customcite{HH21}, cost
reduction, a smaller device footprint, alleviated safety concerns and
leading to diminished image resolution within clinically feasible scan
durations. \customcite{AFL23}

Low-field \gls{mri} systems are predominantly composed of permanent
magnets. Through the connection of these permanent magnets, a consistent
magnetic field of up to \emph{0.35T} can be generated. However, this
achievement comes at the cost of an average system weight of \emph{14t}.
Despite their cost-effectiveness in production and maintenance,
permanent magnets show drawbacks such as high temperature dependence and
used in \gls{mri}s a limited \gls{snr} due to the constrained field
strength. \customcite{NK16}

@@

A Halbach ring of this type is usually based on a ring with permanent
magnets arranged in a circle. Figure
\ref{Example_Halbach_ring_with_cutouts_for_eight_magnets.png} shows an
example \gls{cad} model of such a ring.

@@

The sources for the shimming process can be passive and active based.
Passive shimming uses ferromagnetic metal materials inserted into the
inner magnet bore. \customcite{BPA22} Active shimming, on the other hand,
can use additional coils or existing gradient coils controlled by
special circuitry. Also, software algorithms can be used to adjust the
control parameters of the \gls{mri} system and improve homogeneity
\customcite{WAH21}.

@@

The Halbach magnet incorporated in this system boasts a \emph{27cm}
diameter, a \emph{B0} field strength of \emph{50.4 mT}, and an
impressive homogeneity of \emph{2400 \gls{ppm}} over a \emph{20cm}
diameter using smaller magnets (\(12 x 12 x 12 mm^3\)). \customcite{OTW19}

@@

In order to measure the magnets individually, there are already
implementations that use different measurement methods to determine the
field strength of individual magnets and individual measuring points are
recorded. \customcite{WZC21}

@@

Special algorithms from various, public projects are used to optimize
homogeneity, like a genetic algorithm which O'Reilly implemented
\customcite{O24}. Therefore, the challenge is to ensure the seamless
integration and compatibility of these algorithms into the overall
process. This should make it possible to create a workflow from the
individual magnet to the finished optimized \gls{cad} model of a Halbach
ring. In addition, it is possible to find a selection of suitable
magnets whose magnetic field is as identical as possible

@@

A practical application of the framework is shown, which demonstrates
the characterization of two magnetic field sensors. For this use case,
two sensors were selected to be included in the study. The aim is to use
the framework to verify whether the selected sensors meet the strict
criteria for an accuracy of \emph{1000 \gls{ppm}}. It is also to check
whether the measuring range of these sensors corresponds to the required
field strength and whether they are suitable for the intended
application.

@@

Concerning the \emph{DeLoRI} project, this study exclusively delves into
the realm of permanent magnets employed for creating a homogeneous
\emph{B0} field through Halbach rings. Other systems for measurements
are deliberately excluded from consideration but will be necessary in
later stages of the \emph{DeLoRI} project.

@@

Figure
\ref{Typical_block_diagram_of_a_digital_hall_sensor_sensing_chain_using_three_hall_plates.png}
shows the internal structure of a digital Hall effect sensor as a block
diagram. The Hall effect takes place in the Hall plates. These are
orientated differently depending on the axis inside the \gls{ic}s. In
this case, it is a three-axis hall effect sensor. The output voltage
generated by the Hall plates is then digitised by a \gls{adc}. The
values can then be read out via a digital interface.

@@

\begin{longtable}[]{@{}lllll@{}}
\caption{List of in unified firmware implemented digital magnetic field
sensors with focus on different sensor capabilities.
\label{List_of_in_unified_firmware_implemented_digital_magnetic_field_sensors_with_focus_on_different_sensor_capabilities.csv}}\tabularnewline
\toprule
& TLV493D & HMC5883L & MMC5603NJ & AS5510\tabularnewline
\midrule
\endfirsthead
\toprule
& TLV493D & HMC5883L & MMC5603NJ & AS5510\tabularnewline
\midrule
\endhead
Readout-Axis & 3D & 3D & 3D & 1D\tabularnewline
Temperature-Sensor & yes & no & yes & no\tabularnewline
Resolution {[}uT{]} & 98 & 0.2 & 0.007 & 48\tabularnewline
\gls{dr} {[}mT{]} & ±130.0 & ±0.8 & ±3 & ±50\tabularnewline
Interface & \gls{i2c} & \gls{i2c} & \gls{i2c} & \gls{i2c}\tabularnewline
\bottomrule
\end{longtable}

@@

Table
\ref{List_of_in_unified_firmware_implemented_digital_magnetic_field_sensors_with_focus_on_different_sensor_capabilities.csv}
shows a selection of sensors for which hardware and software support has
been implemented. The resolution of the selected sensors covers the
expected range of values required by the various magnets to be tested.

@@

Figure
\ref{Rendered_mechanical_structure_of_the_1D_sensor_(+cad)_model_with_different_parts_colored_separately,_and_universal_magnet_mount_shown_in_green.png},
shows rendered view of the 1D-Single sensor \gls{cad} drawing, which is
described in chapter \ref{d-single-sensor}. All parts are produced using
3D printing additive manufacturing process. The sensor circuit board is
glued underneath the magnet holder. This is interchangeable, so
different distances between sensor and magnet can be realised. The
exchangeable magnetic holder (shown in green in Figure
\ref{Rendered_mechanical_structure_of_the_1D_sensor_(+cad)_model_with_different_parts_colored_separately,_and_universal_magnet_mount_shown_in_green.png})
can be adapted to different magnets. It can be produced quickly due to
the small number of parts used. The two recesses lock the magnet holder
with the inserted magnet over the sensor. The mechanical design created
is able to accommodate cylinders, cubes, up to a maximum length of
\emph{30mm}. Other magnet shapes require a modification of the base
plate and the sensor holder. The specified tolerances of \emph{0.45mm}
allow the magnet to be inserted into the 3D printed holder with repeat
accuracy and without backlash. This was accomplished with the help of
tolerance tests for the 3D printing material used \gls{pla} and the 3D
printer used \emph{Voron 2.4 350mm} through several series of tests.
This is important if several magnets must be measured, where the
positioning over the sensor must always be the same.

@@

Figure
\ref{Unified_sensor_firmware_program_structure_with_listed_setup_and_main_loop_routines_using_simplified_function_blocks.png}
shows a flow chart of the start process after powering on the sensor and
the subsequent main loop for processing the user commands and sensor
results. When the microcontroller is started, the software checks
whether known sensors are connected to \gls{i2c} or \gls{uart}
interfaces.

@@

\begin{itemize}
\tightlist
\item
  \gls{mrp}-library, is introduced in chapter
  \ref{software-readout-framework}
\item
  Stand-alone mode via sending commands using built-in \gls{cli}
\end{itemize}

The \gls{cli} mode is a simple text-based interface with which it is
possible to read out current measured values, obtain debug information
and set operating parameters. This allows to quickly inspect whether the
hardware is working properly after firmware installation. The command
\emph{help}, displays a detailed command reference with all available
commands as shown in Figure
\ref{Unified_sensor_firmware_provided_serial_terminal_based_(+cli)_allows_the_user_to_configure_the_sensor_manually.png}
to the user.

@@

Figure
\ref{Result_of_an_executed_b_value_measurement_readout_command_using_the_sensors_(+cli)_with_immediate_user_readable_response.png}
shows the current measured value queried by using the \emph{readout}
command by the user.

@@

A jitter time of up to an additional \emph{1ms} is added between the
triggering of the measurements by the host system and the receipt of the
command by the sensor hardware. If the host system is still under load,
this value increases many times over. This means that synchronising
several sensors via the \gls{usb} connection alone is not sufficient.
The other issue is sending the trigger signal from the readout software,
which is described in chapter \ref{software-readout-framework}. At this
point unpredictable latencies can occur, too, depending on which other
tasks are also executed on this port. To enable the most stable possible
synchronisation between several sensors, an option has already been
created to establish an electrical connection between sensors. This is
used together with the firmware to synchronise the readout intervals.
Figure
\ref{Multi_sensor_synchronisation_wiring_example_using_three_sensors_together_with_one_host_(+pc)_performing_the_triggering_and_readout_processing.png}
illustrates the schematic how several sensors must be wired together to
implement this form of synchronisation.

@@

Once the hardware has been prepared, the task of the firmware of each of
the chained sensors is to find a common synchronisation clock. Figure
\ref{Unified_sensor_firmware_multi_sensor_synchronisation_procedure_using_sync_(+gpio)_input_for_operation_(primary_or_secondary)_mode_decision.png}
illustrates how the firmware handles the decision task if the sensor is
\emph{primary} or \emph{secondary} at startup. The internal
firmware-function \emph{register irq on sync pin} is overwritten. To set
one \emph{primary} and several \emph{secondary} sensors, each sensor
waits for an initial pulse on the SYNC-\gls{gpio}, which is a pin at the
microcontroller with the functionality to detect if the sensor is a
primary or a secondary sensor. A random timer is started beforehand by
each sensor, which sends a pulse on the sync line. All others receive
this and switch to \emph{secondary mode} and synchronise the
measurements based on each sync pulse received.

@@

In single-sensor operation, this automatically jumps to \emph{primary}
sensor operation through the \emph{got impulse within 1000ms} branch
result. Figure
\ref{Result_of_the_opmode_command_execution_on_a_sensor_which_is_connected_to_another_as_primary_configured_sensor.png}
shows the synchronisation status of the sensor which can be queried via
the user interface described in chapter \ref{communication-interface} by
using the \emph{opmode} command. An important aspect of the
implementation is that there is no numbering or sequence of the
individual sensors. This means that for the subsequent readout of the
measurements, it is only important that they are taken at the same
interval across all sensors. The sensor differentiation takes place
later in the \gls{mrp}-library \ref{software-readout-framework} by using
the sensor \gls{uuid}.

@@

Table
\ref{Build_hardware_sensors_equipped_with_different_sensor_(+ic)s_to_cover_various_magnet_charaterisation_setups.csv}
shows the various prototype sensor platforms equipped with different
magnetic field sensors. These cover all the required functions described
in the use cases \ref{use-cases}. The most significant difference, apart
from the sensor used, is the \emph{scan mode}. In this context, this
describes whether the sensor can measure a \emph{static} fixed point on
the magnet or if the sensor can move \emph{dynamically} around the
magnet using a controllable manipulator.

@@

Figure
\ref{3D_plot_of_an_N45_12x12x12mm_magnet_using_the_build_3D_full_sphere_sensor_with_visible_magnetic_field_strength_deviations_using_different_shaded_vertices_on_a_sphere.png}
shows the visualisation of such a scan in the form of a spherical 3D
map. On the sphere is the magnetic field strength, which is detected by
the sensor at the position. The transition from a fully positive field
strength (red) to a negative field strength (blue) is clearly
recognisable and corresponds to the orientation of the magnet in the
holder. The magnet sensor is mounted on a movable arm, which can move
\emph{180} degrees around the magnet on one axis. To be able to map the
full sphere, the magnet is mounted on a turntable. This permits the
manipulator to move a polar coordinate system.

@@

For this purpose, the library is divided into individual modules, which
are shown in Figure
\ref{A_high_level_overview_of_all_MRP_library_implemented_Python_modules_which_can_be_changed_by_the_user.png}.
In combination, these represent a typical
measurement-analysis-evaluation workflow of data. For this purpose, a
module system with standardised functional patterns and data types is
developed and packed together in an extendable Python library.

@@

As it is possible to connect many identical sensors to one host,
therefore it needs to be possible to address them separately. This
separation is done by the \emph{MRPProxy} module, which is a separate
part from the core \gls{mrp}-library, to keep installation package
dependencies small. Each connected sensor is accessed via the text-based
\gls{cli}, which is initially the same for each sensor. The only
identification feature is the sensor \gls{uuid} by using the \emph{id}
command of the sensor \gls{cli}. The \emph{MRPProxy} instance claims to
be a sensor to the host \gls{pc} running \gls{mrp} \gls{cli}, so
multiple sensors must be combined into one virtual one. This is done in
several steps, the procedure is described in the following sub-chapters.

@@

A crucial point is the management of the meta data, which further
describes the measurement. This is realised in the example using the
\emph{set\_additional\_data} function. The measurement is exported for
archiving and further processing; various export formats are available.
Using the \emph{dump\_to\_file} function, the measurement can be
converted into a open \gls{json} format.

@@

The main function of the \emph{MRPReading} module is to manage the
measurement and meta-data. The next step is to record and store data
points using hardware sensors. For this purpose, the \emph{MRPHal}
module is developed, which can interact with all \emph{Unified Sensor}
compatible sensors (refer to chapter \ref{unified-sensor}). In the
following example Listing \ref{lst:mrpexample_hal}, an \emph{1D: Single
Sensor}, which is explained in chapter \ref{d-single-sensor}, is
connected locally to the host \gls{pc}. \newpage

@@

The next logical step is to analyse the recorded data. This can involve
one or several hundred data records. Again, the procedure for the user
is to write their own evaluation Python scripts using the
\gls{mrp}-library. This is particularly useful for complex analyses or
custom algorithms, but not necessarily for simple standard tasks such as
bias compensation or graphical plot outputs. For this purpose, \gls{cli}
application is created further, to enable the user to create and execute
complex evaluation pipelines for measurement data without programming.
Figure \ref{Example_measurement_analysis_pipeline.png} shows a typical
measurement data analysis pipeline, which consists of the following
steps:

@@

The documentation has also been uploaded to the
\href{https://magneticreadoutprocessing.readthedocs.io/}{ReadTheDocs}
service. Figure
\ref{MagneticReadoutProcessing_documentation_hosted_on_ReadTheDocs.png}
shows a screenshot of the start page, which also lists separate menu
items for tutorials on the individual functionalities. The process of
creating and publishing the documentation has been automated using
\href{https://github.com/features/actions}{GithubActions}, so that it is
always automatically kept up to date with new features.

@@

Figure
\ref{MRP_evaluation_result_after_find_similar_values_algorithm_execution_in_the_user_defined_pipeline.png}
shows the measured values filtered by the implemented filter algorithm
of Listing \ref{lst:custom_find_similar_values_algorithm}. It can be
seen that out of the initial \emph{10} measurements (upper plot) only
four measurements that are most similar to the \emph{\gls{cog}} mean
value are filtered (lower plot). The number of desired result
measurements are defined here by the parameter \emph{IP\_return\_count}.
It can be seen from the plotted \emph{\gls{cog}} \(\mu\)T mean values
are close to an ideal Magnet with a \emph{\gls{cog}} value of 0\(\mu\)T.
This ideal value is calculated with the function
\emph{MRP.MRPSimulation.generate\_simulated\_reading}, using the same
measurement parameters (\emph{magnet type}, \emph{dimensions},
\emph{sensor distance}) as they correspond to the mechanical structure
of the used hardware sensor in chapter \ref{d-full-sphere}.

@@

The filter algorithm implemented by the user is thus successfully
executed via the user-programmable pipeline. The calculation result is
successfully verified using raw measurement data and the result of the
algorithm and verified using reference measurements. The streamlined
pipeline approach enables the user to re-execute the implemented
measurement pipeline example with further measurement data. Changes to
filter parameters, for example, are also possible without having to
adapt the code. Using this example, all the required functional
capabilities from the chapter \emph{Use cases} \ref{use-cases} of this
implemented solution are demonstrated in their functional capability.

@@

For this evaluation, the sensors listed in Table
\ref{Digital_magnetic_field_sensors_characterised_for_evaluation.csv}
are used for sensor characterisation. The selection of sensors is
described in chapter \ref{sensor-selection}. The additional column for
the \emph{Background Noise} is taken from the respective data sheets of
the sensors and will be verified in the later \emph{Background Noise}
measurement in chapter \ref{sensor-characterisation-background-noise}.
